---
title: "Missing value Imputation"
author: Jinchen Xie
date: 29/Nov/2019
output: 
  html_document:
    theme: paper
    highlight: tango
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(knitr)
library(readxl)
```

# Import Data
```{r}
baseline_30NA <- read_excel("~/Desktop/datasets/processed/Filtered Attributes Baseline.xlsx", sheet = 'updated_folup_NA30_baseline')
```

```{r}
admission_30NA <- read_excel("~/Desktop/datasets/processed/Filtered Attributes Admission.xlsx", sheet = 'NA2030_filtered_admission')
```
admission_lab: only attributes related to lab measurements
```{r Create admission_lab dataframe}
names(admission_30NA)[names(admission_30NA) == "READMISSION_DAYS"] <- "DAYS_READMISSION"

admission_lab <- 
  select(admission_30NA, -ends_with("_DAYS")) %>% 
  select(rID, DAYS_READMISSION, WBC:GLUCOSE)

names(admission_lab)[names(admission_lab) == "NA"] <- "N_A"

admission_lab$DAYS_READMISSION[which(is.na(admission_lab$DAYS_READMISSION))] <- 0
```

```{r}
summary(admission_lab)
```


# Remove Outliers

```{r Deal with outliers}
remove_outliers <- function(admission_lab) {
  for (measure in names(admission_lab)[seq(3,9)]){
    # eliminate outliers
    iqr <- IQR(admission_lab[[measure]], na.rm = TRUE)
    Q <- quantile(admission_lab[[measure]], probs=c(0.25, 0.75), na.rm = TRUE)
    admission_lab[[measure]][which((admission_lab[[measure]] <  (Q[1] - 1.5*iqr)) | (admission_lab[[measure]] > (Q[2]+1.5*iqr)))] <- NA_real_
  }
  return(admission_lab)
}
```

```{r}
admission_lab <- remove_outliers(admission_lab)
```

```{r}
summary(admission_lab)
```
# Impute Measurements

```{r Mean value imputation}
imput_wbc <- admission_lab %>% group_by(rID) %>% 
                summarise(Mean = mean(WBC, na.rm = TRUE))

imput_hgb <- admission_lab %>% group_by(rID) %>% 
                summarise(Mean = mean(HGB, na.rm = TRUE))

imput_cr <- admission_lab %>% group_by(rID) %>% 
                summarise(Mean = mean(CR, na.rm = TRUE))

imput_egfr <- admission_lab %>% group_by(rID) %>% 
                summarise(Mean = mean(EGFR, na.rm = TRUE))

imput_k <- admission_lab %>% group_by(rID) %>% 
                summarise(Mean = mean(K, na.rm = TRUE))
imput_na <- admission_lab %>% group_by(rID) %>% 
                summarise(Mean = mean(N_A, na.rm = TRUE))

imput_glucose <- admission_lab %>% group_by(rID) %>% 
                summarise(Mean = mean(GLUCOSE, na.rm = TRUE))


for (val in seq(1, dim(imput_glucose)[1])) {
  if(dim(admission_lab[(admission_lab$rID == imput_wbc$rID[val]) & (is.na(admission_lab$WBC)),])[1]!=0){
    admission_lab$WBC[which((admission_lab$rID == imput_wbc$rID[val]) & (is.na(admission_lab$WBC)))] <- imput_wbc$Mean[val]
  }else{
    next
  }
}
for (val in seq(1, dim(imput_glucose)[1])) {  
  if(dim(admission_lab[(admission_lab$rID == imput_hgb$rID[val]) & (is.na(admission_lab$HGB)),])[1]!=0){
    admission_lab$HGB[which((admission_lab$rID == imput_hgb$rID[val]) & (is.na(admission_lab$HGB)))] <- imput_hgb$Mean[val]
  }else{
    next
  }
}
for (val in seq(1, dim(imput_glucose)[1])) {  
  if(dim(admission_lab[(admission_lab$rID == imput_cr$rID[val]) & (is.na(admission_lab$CR)),])[1]!=0){
    admission_lab$CR[which((admission_lab$rID == imput_cr$rID[val]) & (is.na(admission_lab$CR)))] <- imput_cr$Mean[val]
  }else{
    next
  }
}
for (val in seq(1, dim(imput_glucose)[1])) { 
  if(dim(admission_lab[(admission_lab$rID == imput_egfr$rID[val]) & (is.na(admission_lab$EGFR)),])[1]!=0){
    admission_lab$EGFR[which((admission_lab$rID == imput_egfr$rID[val]) & (is.na(admission_lab$EGFR)))] <- imput_egfr$Mean[val]
  }else{
    next
  }
}
for (val in seq(1, dim(imput_glucose)[1])) {  
  if(dim(admission_lab[(admission_lab$rID == imput_k$rID[val]) & (is.na(admission_lab$K)),])[1]!=0){
    admission_lab$K[which((admission_lab$rID == imput_k$rID[val]) & (is.na(admission_lab$K)))] <- imput_k$Mean[val]
  }else{
    next
  }
}
for (val in seq(1, dim(imput_glucose)[1])) {  
  if(dim(admission_lab[(admission_lab$rID == imput_na$rID[val]) & (is.na(admission_lab$N_A)),])[1]!=0){
    admission_lab$N_A[which((admission_lab$rID == imput_na$rID[val]) & (is.na(admission_lab$N_A)))] <- imput_na$Mean[val]
  }else{
    next
  }
}
for (val in seq(1, dim(imput_glucose)[1])) {  
  if(dim(admission_lab[(admission_lab$rID == imput_glucose$rID[val]) & (is.na(admission_lab$GLUCOSE)),])[1]!=0){
    admission_lab$GLUCOSE[which((admission_lab$rID == imput_glucose$rID[val]) & (is.na(admission_lab$GLUCOSE)))] <- imput_glucose$Mean[val]
  }else{
    next
  }
}
```

```{r}
imputed.labs <- admission_lab
summary(imputed.labs)
```

*Generate an original admission_lab*
```{r}
admission_lab <- 
  select(admission_30NA, -ends_with("_DAYS")) %>% 
  select(rID, DAYS_READMISSION, WBC:GLUCOSE)

names(admission_lab)[names(admission_lab) == "NA"] <- "N_A"

admission_lab$DAYS_READMISSION[which(is.na(admission_lab$DAYS_READMISSION))] <- 0

admission_lab <- remove_outliers(admission_lab)
```


# Remove patients with missing values

Based on the imputed admission labs data:
```{r}
na.rid.1 <- dplyr::union(imputed.labs[which(is.na(imputed.labs$WBC)),]$rID, imputed.labs[which(is.na(imputed.labs$HGB)),]$rID) 
na.rid.2 <- dplyr::union(imputed.labs[which(is.na(imputed.labs$CR)),]$rID, na.rid.1)
na.rid.3 <- dplyr::union(imputed.labs[which(is.na(imputed.labs$EGFR)),]$rID, imputed.labs[which(is.na(imputed.labs$K)),]$rID)
na.rid.4 <- dplyr::union(imputed.labs[which(is.na(imputed.labs$N_A)),]$rID, imputed.labs[which(is.na(imputed.labs$GLUCOSE)),]$rID)
na.rid.1 <- dplyr::union(na.rid.3, na.rid.4)
na.rid <- dplyr::union(na.rid.1, na.rid.2)

complete.imputed.labs <- imputed.labs[-which(imputed.labs$rID %in% na.rid),]
```


Based on the non-imputed admission labs data:
```{r}
na.rid.1 <- dplyr::union(admission_lab[which(is.na(admission_lab$WBC)),]$rID, admission_lab[which(is.na(admission_lab$HGB)),]$rID) 
na.rid.2 <- dplyr::union(admission_lab[which(is.na(admission_lab$CR)),]$rID, na.rid.1)
na.rid.3 <- dplyr::union(admission_lab[which(is.na(admission_lab$EGFR)),]$rID, admission_lab[which(is.na(admission_lab$K)),]$rID)
na.rid.4 <- dplyr::union(admission_lab[which(is.na(admission_lab$N_A)),]$rID, admission_lab[which(is.na(admission_lab$GLUCOSE)),]$rID)
na.rid.1 <- dplyr::union(na.rid.3, na.rid.4)
na.rid <- dplyr::union(na.rid.1, na.rid.2)

complete.labs <- admission_lab[-which(admission_lab$rID %in% na.rid),]
```

`complete.labs` contains `dim(complete.labs)[1]` admission records of `length(unique(complete.labs$rID))` patients.
`complete.imputed.labs` contains `dim(complete.imputed.labs)[1]` admission records of `length(unique(complete.imputed.labs$rID))` patients.

```{r}
panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- abs(cor(x, y))
    txt <- format(c(r, 0.123456789), digits = digits)[1]
    txt <- paste0(prefix, txt)
    if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor * r)
}
pairs(~WBC + HGB + CR + EGFR + K + N_A + GLUCOSE, data = complete.labs, 
      lower.panel = panel.cor)
```




# consider only patients with >=3 readmissions
```{r}
readmission_counts <- complete.labs %>% group_by(rID) %>% tally()
subset_rID <- readmission_counts[which(readmission_counts$n>2),]$rID

complete.labs.3to15 <- complete.labs[which(complete.labs$rID %in% subset_rID),]
```



# save two dataset into excel file
```{r}
library(openxlsx)

write.xlsx(complete.labs.3to15, '~/Desktop/datasets/processed/admission_labs_3to15.xlsx', sheetName = "No_imputation_3to15",
  col.names = TRUE, row.names = FALSE)
write.xlsx(complete.labs, '~/Desktop/datasets/processed/imputed_admission_labs.xlsx', sheetName = "Mean_imputations",
  col.names = TRUE, row.names = FALSE)
```


# Reshape the dataset for GBTM in STATA

```{r}
library(data.table)
```


```{r}
patients_id <- unique(complete.labs.3to15$rID)

generate_col_names <- function(measure_name, patients_id){
  col_names <- c()
  for (val in patients_id){
    col_names <- append(col_names, paste(measure_name, val, sep="_"))
  }
 return(col_names) 
}

measurement_df <- function(orginial_df, new_df, measure_name){
  col.names <- generate_col_names(measure_name, patients_id)
  names(new_df) <- col.names
  
  for (val in seq(1, length(unique(complete.labs.3to15$rID)))){
    temp_c <- orginial_df[[measure_name]][which(orginial_df$rID == patients_id[val])]
    new_df[[col.names[val]]] <- c(temp_c, rep(NA, nrow(new_df)-length(temp_c)))
  }
  
  return(new_df)
}
```

*generate column names after transpose*
```{r}
change_col_names <- function(measure_name){
  col_names <- c()
  for (val in seq(1,15)){
    col_names <- append(col_names, paste(measure_name, val, sep="_"))
  }
  return(col_names)
}

```


## WBC

```{r}
# wbc_ob <- complete.labs.3to15 %>% select(rID, WBC)
wbc.df <- data.frame(matrix(ncol = length(unique(complete.labs.3to15$rID)), nrow = 15))

wbc.df <- measurement_df(orginial_df = complete.labs.3to15, new_df = wbc.df, measure_name = 'WBC')

wbc.df.t <- transpose(wbc.df)

names(wbc.df.t) <- change_col_names('WBC')
```

```{r}
wbc.df.t.3to8 <- wbc.df.t
temp_list <- c("WBC_10","WBC_11","WBC_12","WBC_13","WBC_14","WBC_15")
for (val in temp_list){
  wbc.df.t.3to8[[val]] <- NULL
}

```


## K

```{r}
k.df <- data.frame(matrix(ncol = length(unique(complete.labs.3to15$rID)), nrow = 15))

k.df <- measurement_df(orginial_df = complete.labs.3to15, new_df = k.df, measure_name = 'K')

k.df.t <- transpose(k.df)

names(k.df.t) <- change_col_names('K')
```


*DAYS_READMISSION*
```{r}
days.df <- data.frame(matrix(ncol = length(unique(complete.labs.3to15$rID)), nrow = 15))
days.df <- measurement_df(orginial_df = complete.labs.3to15, new_df = days.df, measure_name = 'DAYS_READMISSION')

days.df.t <- transpose(days.df)

names(days.df.t) <- change_col_names('days')
```


*# of times of readmission*
```{r}

time.df <- data.frame(matrix(ncol = length(unique(complete.labs.3to15$rID)), nrow = 15))
names(time.df) <- generate_col_names('T', patients_id)

for (val in seq(1, length(unique(complete.labs.3to15$rID)))){
    time.df[[names(time.df)[val]]] <- seq(1,15)
}

time.df.t <- transpose(time.df)
names(time.df.t) <- change_col_names('T')

```

```{r}
time.df.t.3to8 <- time.df.t
temp_list <- c("T_10","T_11","T_12","T_13","T_14","T_15")
for (val in temp_list){
  time.df.t.3to8[[val]] <- NULL
}
```

```{r}
library(openxlsx)
```


*Combine data to save together as 1 dataframe*

```{r}
combined.df.1 <- cbind(wbc.df.t, time.df.t)
write.xlsx(combined.df.1, '~/Desktop/datasets/processed/combined times for gbtm.xlsx', col.names = TRUE, row.names = FALSE)
```


```{r}
combined.df.2 <- cbind(k.df.t, time.df.t)
write.xlsx(combined.df.2, '~/Desktop/datasets/processed/combined times for gbtm.xlsx', col.names = TRUE, row.names = FALSE)
```




```{r}
write.xlsx(wbc.df, '~/Desktop/datasets/processed/wbc for gbtm.xlsx', col.names = TRUE, row.names = FALSE)
write.xlsx(days.df, '~/Desktop/datasets/processed/readmission_days for gbtm.xlsx',col.names = TRUE, row.names = FALSE)
```



# Transform data to censored normal 
```{r}
ggplot(data = complete.labs.3to15, aes(K)) + geom_histogram()
```


```{r}
summary(complete.labs.3to15$K)
complete.labs.3to15$K <- log10(complete.labs.3to15$K)
temp.labs.3to15 <- complete.labs.3to15
```

```{r}
complete.labs.3to15$K[which(temp.labs.3to15$K < 0.5)] <- 0
complete.labs.3to15$K[which(temp.labs.3to15$K >= 0.5 & temp.labs.3to15$K <= 0.55)] <- 1
complete.labs.3to15$K[which(temp.labs.3to15$K >= 0.55 & temp.labs.3to15$K <= 0.6)] <- 2
complete.labs.3to15$K[which(temp.labs.3to15$K >= 0.6 & temp.labs.3to15$K <= 0.65)] <- 3
complete.labs.3to15$K[which(temp.labs.3to15$K >= 0.65 & temp.labs.3to15$K <= 0.7)] <- 4
complete.labs.3to15$K[which(temp.labs.3to15$K > 0.7)] <- 5


```


