---
title: "GBTM_data_processing2"
author: "Jinchen Xie"
date: "6/12/2020"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(knitr)
library(readxl)
library(openxlsx)
library(data.table)
library(Hmisc)
```

# import admission dataset

The dataset used is admission withou 30% NA tolerance. 
```{r}
admission_30NA <- read_excel("~/Desktop/datasets/processed/Filtered Attributes Admission v2.xlsx", sheet = 'Sheet 1')
baseline.df <- read_excel('~/Desktop/datasets/processed/Filtered Baseline imputed.xlsx', sheet = 'Sheet 1')
```


REMOVE admission that the lab measurements were taken after the VAD procedure was done. -->
752  9438 10540
```{r}
# temp1 <- admission_30NA[which((admission_30NA$POST_VAD == 1) &(admission_30NA$POST_VAD_DAYS <admission_30NA$WBC_DAYS)),]$rID
# # order.inv.rid <- intersect(patients_id, temp1)
# order.inv.rid <- c(752, 9438, 10540)
# 
# admission_30NA <- admission_30NA[-which((admission_30NA$rID %in% order.inv.rid) & (admission_30NA$POST_VAD == 1)),]

# View(admission_lab[which(admission_lab$rID %in% order.inv.rid.2),])
# order.inv.rid.2 <- order.inv.rid.2[-4]
# admission_30NA <- admission_30NA[-which((admission_30NA$rID %in% order.inv.rid.2) & (admission_30NA$POST_TRANSPLANT == 1)),]
```




We are only interested in the continuous lab measurements here. **New dataset: admission_lab**


```{r}
names(admission_30NA)[names(admission_30NA) == "READMISSION_DAYS"] <- "DAYS_READMISSION"

admission_lab <- 
  select(admission_30NA, -ends_with("_DAYS")) %>% 
  select(rID, DAYS_READMISSION, WBC:HCT)

admission_procedure <- admission_30NA %>% 
  select(rID, admission_count, POST_VAD, POST_TRANSPLANT, CABG, PCI, IABP, ABLATION, PACEMAKER_IMPLANT, ICD_IMPLANT, BIV_ICD_IMPLANT)

names(admission_lab)[names(admission_lab) == "NA"] <- "N_A"

admission_lab$DAYS_READMISSION[which(is.na(admission_lab$DAYS_READMISSION))] <- 0
```


```{r}
# summary(admission_lab)
# summary(baseline.df$POST_VAD)
```



# Data Transformation
## WBC 


**Normal range of WBC is 4-11. **
*We remove WBC > 40 as outliers. There are 44 admissions with WBC > 50 that got removed.*


```{r}
measure = "WBC"
admission.wbc <- admission_lab
summary(admission_lab[[measure]])

print(dim(admission_lab[which(admission_lab$WBC > 40),]))
admission.wbc[[measure]][which(admission_lab[[measure]]> 40)]  <- NA_real_

# ggplot(data = admission.wbc, aes(WBC)) + geom_histogram(binwidth = 1)
```


```{r}
admission_lab <- admission.wbc
```



## HGB

```{r}
measure = "HGB"
admission.hgb <- admission_lab
summary(admission_lab[[measure]])
# ggplot(data = admission.hgb, aes(HGB)) + geom_histogram()
```

```{r}
admission_lab <- admission.hgb
```


## EGFR
```{r}
measure = "EGFR"
admission.egfr <- admission_lab
summary(admission_lab[[measure]])
# ggplot(data = admission.egfr, aes(EGFR)) + geom_histogram()
dim(admission_lab[which(admission_lab$EGFR > 200),])
admission.egfr[[measure]][which(admission_lab[[measure]]> 200)]  <- NA_real_
# ggplot(data = admission.egfr, aes(EGFR)) + geom_histogram()
```

```{r}
admission_lab <- admission.egfr
```

```{r}
View(admission_lab[which(admission_lab$EGFR<30),])
```




## K
```{r}
measure = "K"
admission.k <- admission_lab
# summary(admission_lab[[measure]])
# ggplot(data = admission.k, aes(K)) + geom_histogram()
```

```{r}
admission_lab <- admission.k
```




## N_A
```{r}
measure = "N_A"
admission.na <- admission_lab
# summary(admission_lab[[measure]])
# ggplot(data = admission.na, aes(N_A)) + geom_histogram()
```


```{r}
admission_lab <- admission.na
```


## GLUCOSE
```{r}
measure = "GLUCOSE"
admission.glucose <- admission_lab
summary(admission_lab[[measure]])
ggplot(data = admission.glucose, aes(GLUCOSE)) + geom_histogram()
```

```{r}
dim(admission_lab[which(admission_lab$GLUCOSE > 500),])
admission.glucose[[measure]][which(admission_lab[[measure]]> 500)]  <- NA_real_
```


```{r}
admission.glucose[[measure]] <- log10(admission.glucose[[measure]])
# 
# ggplot(data = admission.glucose, aes(GLUCOSE)) + geom_histogram() + xlab("log10(glucose)")
```


```{r}
# normalize <- function(x) {
#   return ((x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE)))
# }
# admission.glucose[[measure]] <- normalize(admission.glucose[[measure]])
# ggplot(data = admission.glucose, aes(GLUCOSE)) + geom_histogram() 
```




```{r}
admission_lab <- admission.glucose
```


## PLATELETS

```{r}
measure = "PLATELETS"
admission.platelet <- admission_lab
# summary(admission_lab[[measure]])
# ggplot(data = admission.platelet, aes(PLATELETS)) + geom_histogram()
```

```{r}
dim(admission_lab[which(admission_lab$PLATELETS > 750),])
admission.platelet[[measure]][which(admission_lab[[measure]]> 750)]  <- NA_real_
```

```{r}
admission_lab <- admission.platelet
```


## HCT

```{r}
measure = "HCT"
admission.hct <- admission_lab
# summary(admission_lab[[measure]])
# ggplot(data = admission.hct, aes(HCT)) + geom_histogram()
```

```{r}
admission_lab <- admission.hct
```

# -------
```{r}
rm(admission.wbc, admission.egfr, admission.hgb, admission.k, admission.na, admission.glucose, admission.platelet, admission.hct)
rm(measure)
```



# only >=3 readmissions
```{r}
readmission_counts <- admission_lab %>% group_by(rID) %>% tally()

sub_3to15_rID <- readmission_counts[which((readmission_counts$n>2) & (readmission_counts$n<16)),]$rID
admission_lab.3to15 <- admission_lab[which(admission_lab$rID %in% sub_3to15_rID),]
```



# allow missing at random
```{r}
list_remove <- c()
mea.rm <- vector(mode="list", length=7)
# for each patient exist in the admission_lab.3to5 subset:
for (id in sub_3to15_rID){
  sub.df <- admission_lab.3to15[which(admission_lab.3to15$rID == id),]
  
  num_wbc <- dim(sub.df[-which(is.na(sub.df$WBC)),])[1]
  na_wbc <- dim(sub.df[which(is.na(sub.df$WBC)),])[1]
  num_hgb <- dim(sub.df[-which(is.na(sub.df$HGB)),])[1]
  na_hgb <- dim(sub.df[which(is.na(sub.df$HGB)),])[1]
  num_egfr <- dim(sub.df[-which(is.na(sub.df$EGFR)),])[1]
  na_egfr <- dim(sub.df[which(is.na(sub.df$EGFR)),])[1]
  num_k <- dim(sub.df[-which(is.na(sub.df$K)),])[1]
  na_k <- dim(sub.df[which(is.na(sub.df$K)),])[1]
  num_na <- dim(sub.df[-which(is.na(sub.df$N_A)),])[1]
  na_na <- dim(sub.df[which(is.na(sub.df$N_A)),])[1]
  num_glucose <- dim(sub.df[-which(is.na(sub.df$GLUCOSE)),])[1]
  na_glucose <- dim(sub.df[which(is.na(sub.df$GLUCOSE)),])[1]
  num_platelets <- dim(sub.df[-which(is.na(sub.df$PLATELETS)),])[1]
  na_platelets <- dim(sub.df[which(is.na(sub.df$PLATELETS)),])[1]
  
  if ((num_wbc<3) & (na_wbc!=0)){
    mea.rm[[1]] <- c(mea.rm[[1]], id)
  }
  if ((num_hgb<3) & (na_hgb!=0)){
    mea.rm[[2]] <- c(mea.rm[[2]], id)
  }
  if ((num_egfr<3) & (na_egfr!=0)){
    mea.rm[[3]] <- c(mea.rm[[3]], id)
  }
  if ((num_k<3) & (na_k!=0)){
    mea.rm[[4]] <- c(mea.rm[[4]], id)
  }
  if ((num_na<3) & (na_na!=0)){
    mea.rm[[5]] <- c(mea.rm[[5]], id)
  }
  if ((num_glucose<3) & (na_glucose!=0)){
    mea.rm[[6]] <- c(mea.rm[[6]], id)
  }
  if ((num_platelets<3) & (na_platelets!=0)){
    mea.rm[[7]] <- c(mea.rm[[7]], id)
  }
  
  
  
  if (((num_wbc<3) & (na_wbc!=0)) | ((num_hgb<3) & (na_hgb!=0)) | ((num_egfr<3) & (na_egfr!=0)) |  ((num_k<3) & (na_k!=0)) | ((num_na<3) & (na_na!=0)) | ((num_glucose<3) & (na_glucose!=0)) | ((num_platelets<3) & (na_platelets!=0))){
    list_remove <- append(list_remove, id)
  }else{
    next
  }
}

inter.id <- c()
for (i in sub_3to15_rID){
  if ((i %in% mea.rm[[1]]) & (i %in% mea.rm[[2]]) & (i %in% mea.rm[[3]]) & (i %in% mea.rm[[4]]) & (i %in% mea.rm[[5]]) & (i %in% mea.rm[[6]]) & (i %in% mea.rm[[7]])){
    inter.id <- c(inter.id, i)
  }
}

admission_lab.NArandom <- admission_lab.3to15[-which(admission_lab.3to15$rID %in% list_remove),]
patients_id <- unique(admission_lab.NArandom$rID)
```

 | ((num_hct<3) & (na_hct!=0))
if ((num_hct<3) & (na_hct!=0)){
    mea.rm[[8]] <- c(mea.rm[[8]], id)
  }

```{r}
rm(num_wbc,na_wbc,num_hgb ,na_hgb,num_egfr,na_egfr,num_k,na_k, num_na, na_na, num_glucose, na_glucose, na_platelets, num_platelets)
rm(id, i, inter.id, sub_3to15_rID, sub.df, readmission_counts, list_remove)
```


**1558 patients left in the cohort.**

# transform procedure attributes
```{r}
admission_procedure <- admission_procedure[which(admission_procedure$rID %in% patients_id),]
admission_procedure.updated <- admission_procedure

for (id in patients_id){
  
  temp.df <- admission_procedure[which(admission_procedure$rID == id),]
  for (val in names(temp.df)[-c(1,2)]){
    if (max(temp.df[val])==1) {
      count <- temp.df[which(temp.df[val]==1),]$admission_count
      if (length(count)>1){
        count <- count[1]
      }

      admission_procedure.updated[which(admission_procedure.updated$rID==id & admission_procedure.updated$admission_count>=count), val] <- 1
    }  
  }
}
```



# -------
# Reshape for traj model input

*Functions used to transform the shape of dataset:*
```{r}
generate_col_names <- function(measure_name, patients_id){
  col_names <- c()
  for (val in patients_id){
    col_names <- append(col_names, paste(measure_name, val, sep="_"))
  }
 return(col_names) 
}

measurement_df <- function(orginial_df, new_df, measure_name){
  col.names <- generate_col_names(measure_name, patients_id)
  names(new_df) <- col.names
  
  for (val in seq(1, length(unique(admission_lab.NArandom$rID)))){
    temp_c <- orginial_df[[measure_name]][which(orginial_df$rID == patients_id[val])]
    new_df[[col.names[val]]] <- c(temp_c, rep(NA, nrow(new_df)-length(temp_c)))
  }
  
  return(new_df)
}

change_col_names <- function(measure_name){
  col_names <- c()
  for (val in seq(1,15)){
    col_names <- append(col_names, paste(measure_name, val, sep="_"))
  }
  return(col_names)
}
```


*WBC*
```{r}
# wbc_ob <- complete.labs.3to15 %>% select(rID, WBC)
wbc.df <- data.frame(matrix(ncol = length(unique(admission_lab.NArandom$rID)), nrow = 15))

wbc.df <- measurement_df(orginial_df = admission_lab.NArandom, new_df = wbc.df, measure_name = 'WBC')

wbc.df.t <-data.table::transpose(wbc.df)

names(wbc.df.t) <- change_col_names('WBC')
```

*HGB*
```{r}
# wbc_ob <- complete.labs.3to15 %>% select(rID, WBC)
hgb.df <- data.frame(matrix(ncol = length(unique(admission_lab.NArandom$rID)), nrow = 15))

hgb.df <- measurement_df(orginial_df = admission_lab.NArandom, new_df = hgb.df, measure_name = 'HGB')

hgb.df.t <-data.table::transpose(hgb.df)

names(hgb.df.t) <- change_col_names('HGB')
```

*EGFR*
```{r}
# wbc_ob <- complete.labs.3to15 %>% select(rID, WBC)
egfr.df <- data.frame(matrix(ncol = length(unique(admission_lab.NArandom$rID)), nrow = 15))

egfr.df <- measurement_df(orginial_df = admission_lab.NArandom, new_df = egfr.df, measure_name = 'EGFR')

egfr.df.t <-data.table::transpose(egfr.df)

names(egfr.df.t) <- change_col_names('EGFR')
```

*K*
```{r}
# wbc_ob <- complete.labs.3to15 %>% select(rID, WBC)
k.df <- data.frame(matrix(ncol = length(unique(admission_lab.NArandom$rID)), nrow = 15))

k.df <- measurement_df(orginial_df = admission_lab.NArandom, new_df = k.df, measure_name = 'K')

k.df.t <-data.table::transpose(k.df)

names(k.df.t) <- change_col_names('K')
```

*N_A*
```{r}
# wbc_ob <- complete.labs.3to15 %>% select(rID, WBC)
n_a.df <- data.frame(matrix(ncol = length(unique(admission_lab.NArandom$rID)), nrow = 15))

n_a.df <- measurement_df(orginial_df = admission_lab.NArandom, new_df = n_a.df, measure_name = 'N_A')

n_a.df.t <-data.table::transpose(n_a.df)

names(n_a.df.t) <- change_col_names('N_A')
```

*GLUCOSE*
```{r}
# wbc_ob <- complete.labs.3to15 %>% select(rID, WBC)
glucose.df <- data.frame(matrix(ncol = length(unique(admission_lab.NArandom$rID)), nrow = 15))

glucose.df <- measurement_df(orginial_df = admission_lab.NArandom, new_df = glucose.df, measure_name = 'GLUCOSE')

glucose.df.t <-data.table::transpose(glucose.df)

names(glucose.df.t) <- change_col_names('GLUCOSE')
```



*PLATELETS*
```{r}
# wbc_ob <- complete.labs.3to15 %>% select(rID, WBC)
platelets.df <- data.frame(matrix(ncol = length(unique(admission_lab.NArandom$rID)), nrow = 15))

platelets.df <- measurement_df(orginial_df = admission_lab.NArandom, new_df = platelets.df, measure_name = 'PLATELETS')

platelets.df.t <- data.table::transpose(platelets.df)

names(platelets.df.t) <- change_col_names('PLATELETS')
```


*HCT*
```{r}
# wbc_ob <- complete.labs.3to15 %>% select(rID, WBC)
# hct.df <- data.frame(matrix(ncol = length(unique(admission_lab.NArandom$rID)), nrow = 15))
# 
# hct.df <- measurement_df(orginial_df = admission_lab.NArandom, new_df = hct.df, measure_name = 'HCT')
# 
# hct.df.t <- data.table::transpose(hct.df)
# 
# names(hct.df.t) <- change_col_names('HCT')
```

*Procedures*
```{r}
procedure.list <- names(admission_procedure.updated)[-c(1,2)]

procedure.df <- data.frame(matrix(ncol = length(unique(admission_procedure.updated$rID)), nrow = 15))
procedure.df <- measurement_df(orginial_df = admission_procedure.updated, new_df = procedure.df, measure_name = procedure.list[1])
procedure.df.t <- data.table::transpose(procedure.df)
names(procedure.df.t) <- change_col_names(procedure.list[1])

for (val in procedure.list[-1]){
  procedure.df.temp <- data.frame(matrix(ncol = length(unique(admission_procedure.updated$rID)), nrow = 15))
  procedure.df.temp <- measurement_df(orginial_df = admission_procedure.updated, new_df = procedure.df.temp, measure_name = val)
  procedure.df.temp.t <- data.table::transpose(procedure.df.temp)
  names(procedure.df.temp.t) <- change_col_names(val)
  procedure.df.t <- cbind(procedure.df.t, procedure.df.temp.t)
}

```


## number of readmissions
```{r}
time.df <- data.frame(matrix(ncol = length(unique(admission_lab.NArandom$rID)), nrow = 15))
names(time.df) <- generate_col_names('T', patients_id)

for (val in seq(1, length(unique(admission_lab.NArandom$rID)))){
    time.df[[names(time.df)[val]]] <- seq(1,15)
}

time.df.t <- data.table::transpose(time.df)
names(time.df.t) <- change_col_names('T')

```



# save dataset

```{r}
combined.labs.time <- cbind(patients_id, wbc.df.t, hgb.df.t, egfr.df.t, k.df.t, n_a.df.t, glucose.df.t, platelets.df.t, time.df.t, procedure.df.t)
write.xlsx(combined.labs.time, '~/Desktop/datasets/processed/GBTM_data/combined gbtm stata data v4.xlsx', col.names = TRUE, row.names = FALSE)
```

```{r}
rm(egfr.df, wbc.df, hgb.df, k.df, k.df.t, n_a.df, glucose.df.t, glucose.df, platelets.df, time.df, time.df.t)
rm(val, generate_col_names, measurement_df, change_col_names)
```


# dataset characteristics
```{r}
# summary(admission_lab.NArandom$WBC)
# ggplot(data = admission_lab.NArandom, aes(WBC)) + geom_histogram()
# 
# summary(admission_lab.NArandom$HGB)
# ggplot(data = admission_lab.NArandom, aes(HGB)) + geom_histogram()
# 
# summary(admission_lab.NArandom$EGFR)
# ggplot(data = admission_lab.NArandom, aes(EGFR)) + geom_histogram()
# 
# summary(admission_lab.NArandom$K)
# ggplot(data = admission_lab.NArandom, aes(K)) + geom_histogram()
# 
# summary(admission_lab.NArandom$GLUCOSE)
# ggplot(data = admission_lab.NArandom, aes(GLUCOSE)) + geom_histogram()
# 
# summary(admission_lab.NArandom$N_A)
# ggplot(data = admission_lab.NArandom, aes(N_A)) + geom_histogram()
# 
# summary(admission_lab.NArandom$PLATELETS)
# ggplot(data = admission_lab.NArandom, aes(PLATELETS)) + geom_histogram()
```

**How many readings available at each readmission times?**

# missing CHECK



```{r}
combined.labs.time %>% select(starts_with("N_A_")) %>% 
  summarise_all(funs(na = sum(is.na(.))/(dim(combined.labs.time)[1]), left = sum(!is.na(.))))
```


```{r}
df <- read_excel("~/Desktop/trial save.xlsx", sheet="Sheet1")
```


# identify patients in each traj group
```{r}
groups <- sort(unique(df$`_traj_Group`))
pat.membership <- vector(mode="list", length = length(groups))
for (group in groups){
  pat.membership[[group]] <- df$patients_id[which(df$`_traj_Group`==group)]
}
```


### WBC
```{r}
wbc.t <- cbind(patients_id, wbc.df.t)

na.percol <- vector(mode="list", length=length(pat.membership))

for (i in 1:length(pat.membership)){
  wbc.groups <- wbc.t[which(wbc.t$patients_id %in% pat.membership[[i]]),]
  na.percol[[i]] <- wbc.groups %>% select(starts_with("WBC_")) %>% 
    summarise_all(funs(sum(is.na(.))/(dim(wbc.groups)[1])))
}

for (i in 1:length(pat.membership)){
  sub.percol <- data.frame(t(na.percol[[i]]))
  names(sub.percol) <- c("num_na")
  print(ggplot(data = sub.percol, aes(x=1:15, y=num_na)) + geom_line(linetype = "dashed") + geom_point() + xlab("times of admission") + ylab("% NA value")+ scale_y_continuous(breaks = seq(0, 1, 0.1)))
}
```

### NA
```{r}
n_a.t <- cbind(patients_id, n_a.df.t)

na.percol <- vector(mode="list", length=length(pat.membership))

for (i in 1:length(pat.membership)){
  n_a.groups <- n_a.t[which(n_a.t$patients_id %in% pat.membership[[i]]),]
  na.percol[[i]] <- n_a.groups %>% select(starts_with("N_A_")) %>% 
    summarise_all(funs(sum(is.na(.))/(dim(n_a.groups)[1])))
}

for (i in 1:length(pat.membership)){
  sub.percol <- data.frame(data.table::transpose(na.percol[[i]]))
  names(sub.percol) <- c("num_na")
  print(ggplot(data = sub.percol, aes(x=1:15, y=num_na)) + geom_line(linetype = "dashed") + geom_point() + xlab("times of admission") + ylab("% NA value")+ scale_y_continuous(breaks = seq(0, 1, 0.1)))
}
```

