---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(VennDiagram)
library(RColorBrewer)
```



# EGFR single traj 

```{r}
egfr.no.tcov <- readxl::read_excel("/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 18/traj_results/egfr_single.xlsx")
```

In EGFR single trajectory, Group 1 is the highest risk group.
In Multi-traj, Group 2 is the highest risk group.
We would like to examine how many patients are in the highest risk group for both of them.
```{r}
multi.risky <- multitraj.no.tcov[which(multitraj.no.tcov$`_traj_Group`==2),]
egfr.risky <- egfr.no.tcov[which(egfr.no.tcov$`_traj_Group`==1),]

risky1 <- multi.risky[which(multi.risky$patients_id %in% egfr.risky$patients_id),]
dim(risky1)[1]/dim(multi.risky)[1]
```

There are 259 patients in the highest risk group in multi-traj who are also in the highest risk group for single egfr traj.

```{r}
egfr.single.outcomes<- readxl::read_excel("/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 18/egfr_single_withoutcome.xlsx")
```

```{r}

egfr.single.outcomes$CTB_predicted <- 0
egfr.single.outcomes[which(egfr.single.outcomes$`_traj_Outcome`>0.5),]$CTB_predicted <- 1
summary(egfr.single.outcomes$CTB_predicted)


dim(egfr.single.outcomes[which(egfr.single.outcomes$GC == egfr.single.outcomes$CTB_predicted),])[1]/1653
```

# Multi-traj model result

```{r}
cohort.ids <- readxl::read_excel("/Users/jinchenxie/Desktop/HF_Research/datasets/subset1653.xlsx")
# multitraj.no.tcov <- readxl::read_excel("/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 18/traj_results/multi_no_tcov.xlsx")
multi.full <- readxl::read_excel("/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 18/traj_results/multi_full.xlsx")
```
## VAD
`group.1` is the dataframe that contains all GBTM results of Group 1.
`vad.ids` is the patient ids of patient who got VAD intervention.
`no.vad.ids` is the patient ids of patient who didn't get VAD intervention.

```{r}
group.1 <- multi.full[which(multi.full$`_traj_Group` == 5),]
# group.1 <- multi.full
ids <- group.1$patients_id
group.1.vad <- group.1 %>% select(patients_id, starts_with("POST_VAD"))

group.1.vad$POST_VAD <- group.1.vad %>% select(starts_with("POST_VAD")) %>% rowSums(na.rm=TRUE)
group.1.vad[which(group.1.vad$POST_VAD > 0),]$POST_VAD <- 1
```

```{r}
vad.ids <- group.1.vad[which(group.1.vad$POST_VAD > 0),]$patients_id
no.vad.ids <- group.1.vad[which(group.1.vad$POST_VAD == 0),]$patients_id

length(vad.ids)
length(no.vad.ids)

no.vad.ave <- group.1[which(group.1$patients_id %in% no.vad.ids),] %>% 
    select(starts_with('EGFR_')) %>% colMeans(na.rm=TRUE) %>% as.data.frame()
no.vad.ave$type <- "no vad"
no.vad.ave$adm <- 1:10
# vad.df <- no.vad.ave
# colnames(vad.df) <- 
vad.ave <- group.1[which(group.1$patients_id %in% vad.ids),] %>% 
    select(starts_with('EGFR_')) %>% colMeans(na.rm=TRUE) %>% as.data.frame()
vad.ave$type <- "with vad"
vad.ave$adm <- 1:10
vad.total.ave <- group.1[which((group.1$patients_id %in% vad.ids) | (group.1$patients_id %in% no.vad.ids)),] %>% 
    select(starts_with('EGFR_')) %>% colMeans(na.rm=TRUE) %>% as.data.frame()
vad.total.ave$type <- "total"
vad.total.ave$adm <- 1:10


```

```{r}
df.plot <- rbind(no.vad.ave, vad.ave, vad.total.ave)
colnames(df.plot) <- c("val", "type", "adm")
ggplot(df.plot, aes(x=adm, y=val, color=type)) + geom_line() + scale_color_discrete(name = "Groups") + 
  scale_x_continuous(breaks=1:10) + ylab("Average EGFR Level")
ggsave("/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 20/tcov_g5_vad_egfr_plot.png", width = 7, height = 4)
```


## HTX

```{r}
group.1 <- multi.full[which(multi.full$`_traj_Group` == 5),]
ids <- group.1$patients_id
group.1.htx <- group.1 %>% select(patients_id, starts_with("POST_HTX"))

group.1.htx$POST_HTX <- group.1.htx %>% select(starts_with("POST_HTX")) %>% rowSums(na.rm=TRUE)
group.1.htx[which(group.1.htx$POST_HTX > 0),]$POST_HTX <- 1
```

```{r}

htx.ids <- group.1.htx[which(group.1.htx$POST_HTX > 0),]$patients_id
no.htx.ids <- group.1.htx[which(group.1.htx$POST_HTX == 0),]$patients_id

length(htx.ids)
length(no.htx.ids)

no.htx.ave <- group.1[which(group.1$patients_id %in% no.htx.ids),] %>% 
    select(starts_with('EGFR_')) %>% colMeans(na.rm=TRUE) %>% as.data.frame()
no.htx.ave$type <- "no htx"
no.htx.ave$adm <- 1:10
# htx.df <- no.htx.ave
# colnames(htx.df) <- 
htx.ave <- group.1[which(group.1$patients_id %in% htx.ids),] %>% 
    select(starts_with('EGFR_')) %>% colMeans(na.rm=TRUE) %>% as.data.frame()
htx.ave$type <- "with htx"
htx.ave$adm <- 1:10
htx.total.ave <- group.1[which((group.1$patients_id %in% htx.ids) | (group.1$patients_id %in% no.htx.ids)),] %>% 
    select(starts_with('EGFR_')) %>% colMeans(na.rm=TRUE) %>% as.data.frame()
htx.total.ave$type <- "total"
htx.total.ave$adm <- 1:10

df.plot <- rbind(no.htx.ave, htx.ave, htx.total.ave)
colnames(df.plot) <- c("val", "type", "adm")
ggplot(df.plot, aes(x=adm, y=val, color=type)) + geom_line() + scale_color_discrete(name = "Groups") + 
  scale_x_continuous(breaks=1:10) + ylab("Average EGFR Level")
# ggsave("/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 20/tcov_g5_htx_egfr_plot.png", width = 7, height = 4)
```


## Either Interventions
```{r}
group.1 <- multi.full[which(multi.full$`_traj_Group` == 5),]
ids <- group.1$patients_id
group.1.inter <- group.1 %>% select(patients_id, starts_with("POST_HTX"), starts_with("POST_VAD"))

group.1.inter$POST_HTX <- group.1.inter %>% select(starts_with("POST_HTX")) %>% rowSums(na.rm=TRUE)
group.1.inter$POST_VAD <- group.1.inter %>% select(starts_with("POST_VAD")) %>% rowSums(na.rm=TRUE)
group.1.inter$POST_INTER <- 0
group.1.inter[which(group.1.inter$POST_HTX > 0),]$POST_INTER <- 1
group.1.inter[which(group.1.inter$POST_VAD > 0),]$POST_INTER <- 1
```

```{r}
inter.ids <- group.1.inter[which((group.1.inter$POST_HTX > 0)|(group.1.inter$POST_VAD > 0)),]$patients_id
no.inter.ids <- group.1.inter[which((group.1.inter$POST_HTX == 0)&(group.1.inter$POST_VAD == 0)),]$patients_id

length(inter.ids)
length(no.inter.ids)

no.inter.ave <- group.1[which(group.1$patients_id %in% no.inter.ids),] %>% 
    select(starts_with('EGFR_')) %>% colMeans(na.rm=TRUE) %>% as.data.frame()
no.inter.ave$type <- "no intervention"
no.inter.ave$adm <- 1:10
# htx.df <- no.htx.ave
# colnames(htx.df) <- 
inter.ave <- group.1[which(group.1$patients_id %in% inter.ids),] %>% 
    select(starts_with('EGFR_')) %>% colMeans(na.rm=TRUE) %>% as.data.frame()
inter.ave$type <- "with intervention"
inter.ave$adm <- 1:10

inter.total.ave <- group.1[which((group.1$patients_id %in% inter.ids) | (group.1$patients_id %in% no.inter.ids)),] %>% 
    select(starts_with('EGFR_')) %>% colMeans(na.rm=TRUE) %>% as.data.frame()
inter.total.ave$type <- "total"
inter.total.ave$adm <- 1:10
```

```{r}
df.plot <- rbind(no.inter.ave, inter.ave, inter.total.ave)
colnames(df.plot) <- c("val", "type", "adm")
ggplot(df.plot, aes(x=adm, y=val, color=type)) + geom_line() + scale_color_discrete(name = "Groups") + 
  scale_x_continuous(breaks=1:10) + ylab("Average EGFR Level")
ggsave("/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 20/tcov_g5_inter_egfr_plot.png", width = 7, height = 4)
```
# Comparisons between EGFR single and multi-traj analysis

```{r}
multitraj.no.tcov <- readxl::read_excel("/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 18/traj_results/multi_no_tcov.xlsx")
egfr.no.tcov <- readxl::read_excel("/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 18/traj_results/egfr_single.xlsx")
```


```{r}
high.1.egfr <- egfr.no.tcov[which(egfr.no.tcov$`_traj_Group`==1),]$patients_id
high.2.egfr <- egfr.no.tcov[which(egfr.no.tcov$`_traj_Group`==2),]$patients_id
high.3.egfr <- egfr.no.tcov[which(egfr.no.tcov$`_traj_Group`==5),]$patients_id
high.4.egfr <- egfr.no.tcov[which(egfr.no.tcov$`_traj_Group`==3),]$patients_id
high.5.egfr <- egfr.no.tcov[which(egfr.no.tcov$`_traj_Group`==4),]$patients_id
high.1.multi <- multitraj.no.tcov[which(multitraj.no.tcov$`_traj_Group`==2),]$patients_id
high.2.multi <- multitraj.no.tcov[which(multitraj.no.tcov$`_traj_Group`==1),]$patients_id
high.3.multi <- multitraj.no.tcov[which(multitraj.no.tcov$`_traj_Group`==5),]$patients_id
high.4.multi <- multitraj.no.tcov[which(multitraj.no.tcov$`_traj_Group`==3),]$patients_id
high.5.multi <- multitraj.no.tcov[which(multitraj.no.tcov$`_traj_Group`==4),]$patients_id
```

```{r}
myCol <- brewer.pal(2, "Pastel2")
# for highest risk group
graph1 <- venn.diagram(
  list(high.5.egfr, high.5.multi),
  category.names = c("EGFR single" , "Multi-trajectory"),
  # filename = 'high5_venn_diagramm.png',
  filename = '/Users/jinchenxie/Desktop/HF_Research/Weekly Progress/week 20/high5_venn_diagramm.png',
  output = FALSE,
   # Output features
  imagetype="png",
  height = 480, 
  width = 580, 
  resolution = 300,
  # compression = "lzw",
  
  # Circles
  lwd = 2,
  lty = 'blank',
  fill = myCol[1:2],
  cex = .6,
  cat.cex = 0.6,
  cat.just = list(c(0.8, 0) , c(0.2, 0))
)
graph1
```


